Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-08-31 reanalysis-4-propensity_scores.qmd
n cores bug

# Set up parallel processing
# Reduce cores for memory-intensive GBM models
available_cores <- detectCores()
# Use fewer cores to avoid memory issues - each GBM model needs substantial memory
# Don't subtract 1 from max_cores_for_ps since it's already the desired limit
n_cores <- if (available_cores > max_cores_for_ps) max_cores_for_ps else max(1, available_cores - 1)
log_message(paste0("Parallel processing: Using ", n_cores, " cores (of ", available_cores, " available) to manage memory usage"))

@@

# Use mclapply on Unix/Mac, parLapply on Windows
if (.Platform$OS.type == "unix") {
  # Unix/Mac - use mclapply
  parallel_results <- mclapply(
    1:n_imputations,
    function(i) {
      node_id <- imputation_node_assignments$node_id[i]
      process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, node_id, log_file)
    },
    mc.cores = n_cores
  )
} else {
  # Windows - use parLapply
  cl <- makeCluster(n_cores)

>>>>

# Set up parallel processing
# Reduce cores for memory-intensive GBM models
available_cores <- detectCores()
log_message(paste0("Detected ", available_cores, " available cores"))
log_message(paste0("Max cores configured: ", max_cores_for_ps))
# Use fewer cores to avoid memory issues - each GBM model needs substantial memory
# Don't subtract 1 from max_cores_for_ps since it's already the desired limit
n_cores <- if (available_cores > max_cores_for_ps) max_cores_for_ps else max(1, available_cores - 1)
log_message(paste0("Parallel processing: Using ", n_cores, " cores (of ", available_cores, " available) to manage memory usage"))

@@

# Use mclapply on Unix/Mac, parLapply on Windows
if (.Platform$OS.type == "unix") {
  # Unix/Mac - use mclapply
  parallel_results <- mclapply(
    1:n_imputations,
    function(i) {
      node_id <- imputation_node_assignments$node_id[i]
      process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, node_id, log_file)
    },
    mc.cores = n_cores
  )
} else {
  # Windows - use parLapply
  log_message(paste0("Creating cluster with ", n_cores, " workers"))
  cl <- makeCluster(n_cores)
  log_message(paste0("Cluster created with ", length(cl), " workers"))
